---
title: "R Notebook"
output: html_notebook
---


```{r Front Matter, include=FALSE}
# Clean up environment
rm(list = ls())

# Load packages
library(tidyverse)
library(readr)

```

# Add Data Table One

```{r}
fed_data <- 
  read_csv("dif source join.csv")

 View(fed_data)

```

# Add Data Table Two

```{r}
NCANDS <- 
  read_csv("Findings from NCANDS - Data Tables (updated with FY 2015).csv")

View(NCANDS)

```



## Cleaning Federal Data

```{r}





```

## Cleaning NCANDS Data

```{r}

NCANDS <-
  NCANDS %>%
  rename(Characteristic_Label = `Characteristic Label`) %>%
  group_by(State)


```

```{r}

NCANDS_subType <-
  NCANDS %>%
  filter(Table == "Child Fatalities by Submission Type")

NCANDS_Trend <-
  NCANDS %>%
  filter(Table == "Child Fatalities, Trend")

NCANDS_Age <-
  NCANDS %>%
  filter(Table == "Child Victims by Age")

```
55
36
56
 
mWhite <-
57
 
  injuryMortality[c((22:26) , (28:31)), ]
58
37

```




Outline 

# Join

* Join tables from two different sources 


# Data Wrangling Portion

* General purpose data wrangling
    + Use when tidying data tables 
* Use of spread and gather 
* Use of regular expressions
* User-defined functions
* Loops and/or control flow 

# Data Visualization

* Visualization with layered data from distinct data structures
* Visualization displaying 3 or more variables
"* Another visualization
* Another visualization

# Data Analysis

* Statistical modeling/Supervised learning
* Unsupervised learning
* Analysis of text data 










































