---
title: "R Notebook"
output: html_notebook
---


```{r Front Matter, include=FALSE}
# Clean up environment
rm(list = ls())

# Load packages
library(tidyverse)
library(readr)

```

# Add Data Table One

```{r}
fed_data <- 
  read_csv("dif source join.csv")

 View(fed_data)

```

# Add Data Table Two

```{r}
NCANDS <- 
  read_csv("Findings from NCANDS - Data Tables (updated with FY 2015).csv")

View(NCANDS)

```



## Cleaning Data

```{r}


```





Outline 

# Join

* Join tables from two different sources 


# Data Wrangling Portion

* General purpose data wrangling
    + Use when tidying data tables 
* Use of spread and gather 
* Use of regular expressions
* User-defined functions
* Loops and/or control flow 

# Data Visualization

* Visualization with layered data from distinct data structures
* Visualization displaying 3 or more variables
* Another visualization
* Another visualization

# Data Analysis

* Statistical modeling/Supervised learning
* Unsupervised learning
* Analysis of text data 










































