---
title: "R Notebook"
output: html_notebook
---


```{r Front Matter, include=FALSE}

rm(list = ls())

# load packages
library(readxl)
library(readr)
library(rvest)

# scrape data
page <- "https://www.childstats.gov/americaschildren/tables/phy8b.asp"
xpath <- '/html/body/div/table'


table_list <-
  page %>%
  read_html() %>%
  html_nodes(xpath = xpath) %>%
  html_table(fill = TRUE)


injuryMortality <-
  table_list[[1]]

```

## Cleaning Data

```{r}

head(injuryMortality)

```

The above table is not tidy in the sense that the first column contains all the variables; the year variable is spread throughout each row instead of just in one column; there are tables that need to be separated for convenience; the first row has repeating information that is true for all the data and is therefore not necessary in the l itself.

TRAR - total rate all races
TRARM - total rate all races; male
mWhite - white males
mBnon - black non-hispanic males

```{r}

totalRateAllRaces <-
  injuryMortality[c((4:8), (10:13)), ]

TRARMale <-
  injuryMortality[16:20, ]

mWhite <-
  injuryMortality[c((22:26) , (28:31)), ]


mBnon <-
  injuryMortality[c((33:37), (39:42)), ]


mAsianPacific <-
  injuryMortality[c((44:48), (50:53)), ]


mAPnon <-
  injuryMortality[c((55:59), (61:64)), ]

```



Outline 

# Join

* Join tables from two different sources 


# Data Wrangling Portion

* General purpose data wrangling
    + Use when tidying data tables 
* Use of spread and gather 
* Use of regular expressions
* User-defined functions
* Loops and/or control flow 

# Data Visualization

* Visualization with layered data from distinct data structures
* Visualization displaying 3 or more variables
* Another visualization
* Another visualization

# Data Analysis

* Statistical modeling/Supervised learning
* Unsupervised learning
* Analysis of text data 










































