---
title: "R Notebook"
output: html_notebook
---


```{r Front Matter, include=FALSE}

rm(list = ls())

# load packages
library(readxl)
library(readr)
library(rvest)

# scrape data
page <- "https://www.childstats.gov/americaschildren/tables/phy8b.asp"
xpath <- '/html/body/div/table'


table_list <-
  page %>%
  read_html() %>%
  html_nodes(xpath = xpath) %>%
  html_table(fill = TRUE)


injuryMortality <-
  table_list[[1]]

```

## Cleaning Data

```{r}

head(injuryMortality)

```

The above table is not tidy in the sense that the first column contains all the variables; the year variable is spread throughout each row instead of just in one column; there are tables that need to be separated for convenience; the first row has repeating information that is true for all the data and is therefore not necessary in the dataset itself.

TRAR - total rate all races
TRARM - total rate all races; male
mWhite - white males
mBnon - black non-hispanic males

```{r}

totalRateAllRaces <-
  injuryMortality[4:8, ]

leadCauseAllRaces <-
  injuryMortality[10:13, ]

TRARMale <-
  injuryMortality[16:20, ]

mWhite <-
  injuryMortality[22:26, ]

leadMWhite <-
  injuryMortality[28:31, ]

mBnon <-
  injuryMortality[33:37, ]

leadMBnon <-
  injuryMortality[39:42, ]

mAsianPacific <-
  injuryMortality[44:48, ]

leadMAsianPacific <-
  injuryMortality[50:53, ]

mAPnon <-
  injuryMortality[55:59, ]

leadMAPnon <-
  injuryMortality[61:64, ]

mHispanic <-
  injuryMortality[66:70, ]

leadMHispanic <-
  injuryMortality[]



```












































