---
authors:  Funke Alliyu and Lauryn Pavlik
due date: April 30th, 2019
title: "R Notebook"
output: html_notebook
---


```{r Front Matter, include=FALSE}
# Clean up environment
rm(list = ls())

# Load packages
library(tidyverse)
library(readr)

```

# Add Data Table One

```{r}
fed_data <- 
  read_csv("dif source join.csv")

 head(fed_data)

```

# Add Data Table Two

```{r}
NCANDS <- 
  read_csv("Findings from NCANDS - Data Tables (updated with FY 2015).csv")

head(NCANDS)

```



## Cleaning Federal Data

### Making a totals table 

```{r}
# Make totals seperate table from fed_data
fed_totals <-
  fed_data %>%
  filter(`Measure 2` == "Total")

```

```{r}
# Clean fed_totals
fed_totals <- 
  fed_totals %>%
  rename(Measure_2 = 'Measure 2',  Measure_1 = 'Measure 1') %>%
  spread(key = Format, value = Value) 

```

```{r}
# Remove columns
fed_totals <- 
  fed_totals %>%
  select(-'X7', -'Measure_1', -'Measure_2')

```

```{r}
# Rename remaining variables
fed_totals <- 
  fed_totals %>%
  rename(Num_Fatalities = 'Number', Rate_per_100000 = 'Rate per 100,000 Children')

```

### Cleaning original table

```{r}
# Rename and spread
fed_data <- 
  fed_data %>%
  rename(Measure_2 = 'Measure 2',  Measure_1 = 'Measure 1') %>%
  spread(key = Measure_2, value = Value) %>%
  spread(key = Format, value = Total) %>%
  select(-`Rate per 100,000 Children`, -`X7`)

```

```{r}
# Remove rows (MAYBE WRITE LOOP)
fed_data <- 
  fed_data[-c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20, 22, 24, 26, 28, 30, 32, 34, 36, 38, 40,
              42, 44, 46, 48, 50, 52, 54, 56, 58, 60, 62, 64, 66, 68, 70, 72, 74, 76, 78,
              80, 82, 84, 86, 88, 90, 92, 94, 96, 98, 100), ]

```

```{r}
# Finish cleaning
fed_data[is.na(fed_data)] = 0

fed_data <- 
  fed_data %>%
  rename(Num_agencyfile = `Reported in the Agency File`, 
         Num_childfile = `Reported in the Child File`, 
         Total = Number) %>%
  select(-`Measure_1`)
  
  
```

## Cleaning NCANDS Data

```{r}

NCANDS <-
  NCANDS %>%
  rename(Characteristic = `Characteristic Label`)

```


```{r}

fatality_sub_type <-
  NCANDS %>%
  filter(Table == "Child Fatalities by Submission Type") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


fatality_trend <-
  NCANDS %>%
  filter(Table == "Child Fatalities, Trend") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


victim_age <-
  NCANDS %>%
  filter(Table == "Child Victims by Age") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


case_type <-
  NCANDS %>%
  filter(Table == "Children by Disposition") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


investigation <-
  NCANDS %>%
  filter(Table == "Children Who Received an Investigation or Alternative Response, Trend") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


mal_type <-
  NCANDS %>%
  filter(Table == "Maltreatment Types of Victims") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


perpetrator_tally <-
  NCANDS %>%
  filter(Table == "Perpetrators by Relationship to their Victims") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


perpetrator_total <-
  NCANDS %>%
  filter(Table == "Perpetrators, Trend") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)


referral_Type <-
  NCANDS %>%
  filter(Table == "Screened-In and Screened-Out Referrals") %>%
  spread(key = Measure, value = Value) %>%
  select(-Table)

```




Outline 

# Join

* Join tables from two different sources 


# Data Wrangling Portion

* General purpose data wrangling
    + Use when tidying data tables 
* Use of spread and gather 
* Use of regular expressions
* User-defined functions
* Loops and/or control flow 

# Data Visualization

* Visualization with layered data from distinct data structures
* Visualization displaying 3 or more variables
"* Another visualization
* Another visualization

# Data Analysis

* Statistical modeling/Supervised learning
* Unsupervised learning
* Analysis of text data 










































